\documenttype{article}
\usepackage[utf-8]{inputenc}
\usepackage[english]{babel}
\usepackage[letterpaper]{geometry}
\usepackage{fancyhdr}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{xcolor}
\usepackage{dirtytalk}
\lhead{Discrimination in Schools}
\rhead{Alan Grey}
\rfoot{\thepage}
\title{Discrimination in Schools}
\author{Alan Grey}
\date{}
\pagestyle{fancy}
\begin{document}
\maketitle
\thispagestyle{fancy}

\section{Disclaimer}
This was bassed off of his personall experiance
and may be an exageration. The exact names and 
actions of these people are lost to history.
This is our best guess. All that we can verify
is that it takes place in the United States,
and that this occured often.

\section{Conformity}
They would constantly threaten me. Like I was
their slave. Forced to do what I'm told. No
phones. If they see a phone, you get a warning.
After that, they will take it, and smash it.

There is only conformity. If you don't do it
the way they tell you to, it is wrong. its
always $1+0.2$. $0.2+1$ was wrong and $1.2$ 
didn't show work. All extentions and apps
were blocked. We were forced to have a
spesific desktop background with an omenous
message. I don't remember what is was but
it was somthing like \say{Prepare yourselves}
and it soubtly implied they were useing us
or more likely our computers as lab rats.
Probibly for spyware. 

They can lock you out of your chromebook
at will. This sounds like a good thing
if it is stolen but every 9 weeks, at the
end of the grading period, they will lock
some peoples chromebooks and some of them
will even be held for ransom. 

You arn't alloud to put stickers on your
chromebook. The stickey stuff gets stuck
on it and its hard to clean off. You
also can't use stickers on the charger. 
Even if its a label with your name on it,
its not alloued. If they can't clean it off,
they can just buy a new one. These chargers
are dirt cheap. 

One thing that is unblocked is a basic paint
program wich I use for all the artwork I have
posted online so far.

\section{About the author}
Born on January 3, 2000, Alan Grey is an entrapanur 
and animator. He has been drawing for a long time now 
and is just now makeing his presence known. He is 
\texttt{computer-cat1} on FurAffinity.

Nobody knows his real name and age but he is suspcted
to be best friends with Ivan Flores.

\end{docuemnt}
Does this make me a whistle blower???
...
Yeah it does
