\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage{fancyhdr}
\fancyhf{}
\lhead{RECRIATIONAL DREAMERS}
\rhead{CRIZ ALAN}
\title{Recreational Dreamers Script}
\author{Criz Alan / computer-cat1}
\date{December 2021}

\begin{document}

\maketitle
\tableofcontents

\section{Premise}

A teenager named Alan is discovering the concept of lucid dreaming With his fictional friend,
EEV the\ldots{} the\ldots{} well, She is constantly changing but eventually settles on being
Void the Vaporeon. She will be referred to as EEV (they/them) BEFORE the change and Void (she/her) AFTER.

Depending on how we make the movie, We could end up giving our actors vivid dreams.

Everytime the camera moves, A new scene begins. 

\section{Part One: Introduction}
\subsection[001 - I]{Scene I}

(Alan is sitting in his room, filming in a vlog like style)

\noindent
(To Camera)\\
ALAN: Hello. My name is Alan and I have a voice inside my head--- Well, everyone does but mine\ldots{} isn't me
Its somebody else. They make their own decisions. I game them a name, EEV, and they said they could find me in my dreams
which was a little creepy but I know they have good intentions---

\noindent
ALAN: Lucid dreaming? Apple Juice? Reality checks? What does that mean? I can't just absorb\ldots{} information\ldots{}

\noindent
ALAN: They're talking again! Wait wait wait! Oooooooh boy I gotta write this down!

\noindent
(He kicks the camera and it stops recording)

\subsection[002 - II]{Scene II}

(Alan is filming from his bed)

\noindent
ALAN: Ok, ok. I got a whole instruction manual here!

\noindent
(He holds up a large stack of paper)\\
(This stack of paper might be this very script for an easter egg.)

\noindent 
ALAN: So uhhhhhhh\ldots{} I spend all of my day on autopilot. If I breakthrough that, I can become self aware in dreams.
I could try reading, pushing my finger through my hand or just looking at my hands in general. Plug my nose and see if I can still breath
These kind of things are reality checks.

\noindent
ALAN: When laying in bed, say a mantra. Simple as that. Oh yeah and (mumbling\ldots{} hallucinations from uhhh) apple juice is helpful don't ask why!

\noindent
ALAN: Also, napping helps your chances by like, a thousand times. I speak of experience \footnote{Nathan, the actor of Alan, claims to only
have vivid dreams when he accidentally falls asleep during the day. Interesting!}

\noindent
ALAN: I need to wait untill night time. so lets just fast forward through school here\ldots{}

\subsection[003 - III]{Scene III}

(Camera is pointing down at a desk with a lot of paper. Mostly consept art from Nathan with some sheet music from KURAIO in there too.)

\noindent
ALAN: Nyeeeeeeehhhhhhhhhh!!!!!

\noindent
(He slides all the paper off the desk and onto the floor)

\noindent
ALAN: Thats better! 

\subsection[004 - IV]{Scene IV}

(Alan is in bed) (He closes his eyes and then suddenly gets up)

\noindent
ALAN: Wait!

\noindent
(He gets a peice of paper and puts it on his night stand)

\noindent
ALAN: Now I'll be ready.

\subsection[005 - V]{Scene V}

(The previous scene fades into darkness. There is a long pause. Then suddenly cuts to this scene)

\noindent
ALAN: What happened?

\noindent
EEV: Not alloud to tell you. You arn't worthy yet.

\noindent
ALAN: What? Why?

\noindent
EEV: Just keep doing what you're doing and you might get lucky. From there it will get easier and easier untill you can do it whenever you want.
\footnote{Most people try to 'Lucid dreem TONIGHT` but that is simply imposible. Like all skills, it takes a lot of practice.}

\section{Part Two: A Single Dream}
\subsection[006 - VI]{Scene VI}

(Alan tries really hard this time.) (He constantly does reality checks. He changes his mantra to 'If I am not in my bed, I am dreaming`
he writes in his journal everyday, even if nohing hapened. And of course, apple juice.)
\footnote{All of these things have been sientifically proven to increse your chances exept apple juice. I personally
am still recearching it IRL}

\subsection[007 - VII]{Scene VII}

(The screen is dark)

\noindent
EEV: Is--- Is that you?

\subsection[008 - VIII]{Scene VIII}

(Alan jumps out of bed)

\noindent
ALAN: Woah!

\noindent
(He frantically writes.)

\noindent
ALAN: Wait\ldots{} Its 4AM?

\subsection[009 - IX]{Scene IX}

(He is in school)

\noindent
MRS.PARKER: ---and guamine.

\noindent
(She turns to the board)

\subsection[010 - X]{Scene X}

(Alan throws a paper spear to Criz.)

\subsection[011 - XI]{Scene XI}

(Close up of Criz unfolding the paper.)

\noindent
(''I have discovered somthing you might want to see. When can I give you my notebook? ``)

\subsection[012 - XII]{Scene XII}

(Criz tosses it back)

\subsection[013 - XIII]{Scene XIII}

(Close up of the paper)

\noindent
(''Dead-drop it at B224 after second period.``)
\footnote{The filming location is B224 and I have that teacher second period.}

\subsection[014 - XIV]{Scene XIV}

(Alan is shaking his head and writes somthing)

\subsection[015 - XV]{Scene XV}

(Meany cuts of them throwing paer to eachother)

\subsection[016 - XVI]{Scene XVI}

(Mrs.Parker turns arround)

\noindent
MRS.PARKER: And thats how DNA---

\noindent
(She makes a strange face)

\subsection[017 - XVII]{Scene XVII}

(Shot of Alan and Criz with paper everywhere)

\subsection[018 - XVIII]{Scene XVIII}

MRS.PARKER: Oh, I want in on this!

\subsection[019 - XIX]{Scene XIX}

(Alan bursts through the door to his room.)

\noindent
ALAN: Here we go again\ldots{}

\subsection[020 - XX]{Scene XX}

(He crashes into his bed and the screen cuts to black)

\section{Part Three: New Found Power}
\subsection[021 - XXI]{Scene XXI}

(Alan is outside on a fild. He is walking like everything is normal.)

\noindent
ALAN: Wait a minute\ldots{} What was I doing five minutes ago?

\noindent
\ldots{}

\noindent
ALAN: This isn't real. It can't be.

\subsection[022 - XXII]{Scene XXII}

(Alan sees an identical copy of himself)

\noindent
ALAN: Ahh!

\noindent
EEV: No No! Don't wake up yet!

\subsection[023 - XXIII]{Scene XXIII}

(He gets up in bed, and sighs)

\noindent
ALAN: Why did I do that\ldots{} (To EEV) Why would you do that!

\noindent
EEV: Do what?

\noindent
ALAN: Why can't you be somthing plesent like\ldots{} like a pokemon.

\noindent
EEV: Look at drawings of pokemon long enough and mabee I'll figure it out.

\noindent
ALAN: Ya know what? I will.

\subsection[024 - XXVI]{Scene XXVI}

(Screen is black then quickly fades to this scene)

(Alan is stting in the xbox room)

\noindent
ALAN: Somhings wrong. Is this how life is suppost to feel? Wait\ldots{}

\noindent
(Yelling)
ALAN: Wheres my brother at?

\noindent
MOM: What brother?

\noindnent
ALAN: Yup this is a dream.

\subsection[025 - XXV]{Scene XXV}

(Camera is pointing at one of the orange boxes. There is a pikachu on it)

EEV: Hei Hei!

\subsection[026 - XXVI]{Scene XXVI}

(Back to alan)

\noindent
ALAN: Not to be rude but I was kinda hoping for somthing else

\subsection[027 - XXVII]{Scene XXVII}

(And back to EEV)

\noindent

\subsection[028 - XXVIII]{Scene XXVIII}
\subsection[029 - XXIX]{Scene XXIX}
\subsection[030 - XXX]{Scene XXX}
\subsection[031 - XXXI]{Scene XXXI}
\subsection[032 - XXXII]{Scene XXXII}
\subsection[033 - XXXIII]{Scene XXXIII}
\subsection[034 - XXXIV]{Scene XXXIV}
\subsection[035 - XXXV]{Scene XXXV}
\subsection[036 - XXXVI]{Scene XXXVI}
\subsection[037 - XXXVII]{Scene XXXVII}
\subsection[038 - XXXVIII]{Scene XXXVIII}
\subsection[039 - XXXIX]{Scene XXXIX}
\subsection{040 - XL]{Scene XL}

%KV needs help nameing scenes so here ya go.

%I=1
%V=5
%X=10
%L=50
%C=100
%M=1000
%A smaller one before a larger one is subtracting
\end{document}
