\documentclass[a5paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{xcolor}
\usepackage{amssymb}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{tabularx}
\usepackage{dirtytalk}
\fancyhf{}
\lhead{\textsc{Turn of a Tide}}
\rhead{\textsc{Page \thepage}}
\cfoot{computer-cat1}
\pagestyle{fancy}
\title{\textsc{Turn of a Tide}}
\author{computer-cat1}
\date{}
\begin{document}
\maketitle
\thispagestyle{fancy}
\section[The Beginning]{Chapter I: The beginning}
I walk up to him, and sit on the stairs.

\say{Kinda cold isn't it?} Daniel says

\say{Yeah} I say. Its only the beginning of November. 
Cant tell him yet, or anyone I guess. Its not like I 
can just unsay it \ldots{}

\say{Soooooo\ldots{}} I look at my watch.

\say{aaaaand NOW its time!} I walk down the hallway 
and we're going the same direction\ldots Of course\ldots

Its that time of the year. Its cold, but not too cold,
and sometimes its not cold at all.
The weather is nice but I've got bigger problems that I 
don't feel like mentioning on the first page of this book.
Because of that I'm going to have to waste some space. 

You
don't know me right? Lets fix that. I'm Alan and I do a 
lot of stuff like lucid dreaming. Lucid dreaming is when
you are dreaming and you know your dreaming so you can
control everything. Its really cool and you can let
your wildest dreams actually be dreams if you know what
your doing. I use it mostly for\ldots{} Are we still
on the first page? We are? Oh uh haha, never mind what
I use this power for, lets talk about computers!

You like computers right? well, so do I! I do animations
of my characters. Sometimes funny, sometimes their on a 
quest and once in a blue moon, another one shows up. 
Their names are--- 

Am I in the clear now? Would it look weird if I were
to leave the rest of this page blank? I'm doing it anyway.
\newpage

For all of human history, 
\end{document}
Thank Kyuu >w<