\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[a5paper,margin=3cm]{geometry}
\usepackage{fancyhdr}
\fancyhf{}
\lhead{Big brother is watching you}
\rhead{Page \thepage}
\cfoot{Cris-Alan gedit.computer-cat1@0box.eu}
\title{They're After Me}
\author{They killed notepad, now I kill them.}
\date{Cris-Alan}
\begin{document}
\maketitle
\pagestyle{fancy}
\thispagestyle{fancy}
\section{Introduction}
\begin{center}
    \emph{''Its not that something is wrong, its that something ha always been wrong, we have just never noticed.``}
\end{center}
Tracking. Does it make you upset that your phone listens to you?
Constantly? Does it make you scared? How about \texttt{malware1}?
You don't remove the virus because I told you its harmless and 
showed you the code for it. What if it could read your browser
history AND close your tabs AND see your screen AND control
what websites you can view, it would be the worst computer virus 
ever!
However, the school district has all these powers from LightSpeed,
Remote-Reset, Relay, and AmazonWebService respectively.

If I can negotiate with my parents, gain the trust of people far 
older and more educated than me, and even convince xxxxxxxx people to tolerate me, I can probably have a talk with the school.

\section{The What}
Meany things I write speeches and letters about are self-evident.
This is no exception. To summarize, students
have no privacy. This hits really personally to me because
I don't exactingly have a home life. I am either at school,
doing school work, or sleeping so I only have access to my own
personal computer on Sundays. This means I have to handle my 
personal agenda (activism, writing, drawing, programming, 
even managing my startup company) on my chromebook which is 
obviously not what it is intended for. Most people play Minecraft
on their chromebooks but I have to handle entire personal life 
on this thing. I've found some solutions: overleaf.com for \LaTeX{}
editing. This is actually how I write this. repl.it helps me work
on github and Tor / Monero / Signal / WhatsApp lets me communicate
with others in an anonymous way and allow me to get the help I 
need. Oh yeah, I would like to believe that blocking DuckDuckGo is a
declaration of war because they exist specifically to provide
people with privacy so blocking it is like declaring no privacy
wich is this case is basically just adding salt to the stab wound.
\section{The Why}
Notepad, Mousepad, GEdit, VIM, Pico, Nano, or on a chromebook,
Text, are simply text editors and have no reason to be blocked.
I understand GB Browser and Co:Writer because they can get around
the block filter but Text? Really?

Allow me to list \emph{every single function} of ''Text``:
\begin{itemize}
    \item Create a blank file
    \item Open any file in a plain text format
    \item Modify the file
    \item Save a file in plain text format, as a new, or over another one.
    \item Syntax highlighting for most programming languages
    \item Ageist text size
    \item Dark theme
\end{itemize}
Thats literally it. What could I possibly do with it. OoOoDoOo 
programming is bAd! You literally gave away 600 chromebooks. Make
up your mind.


\end{document}
