\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage{fancyhdr}
\usepackage{dirtytalk} %Not built in to LaTeX. Just go and google it.
\lhead{STARBASE}
\rhead{ALAN GREY}
\title{Recreational Dreamers Script}
\author{Alan Grey}
\date{Phoenix Studios}
\pagestyle{fancy}
\begin{document}
\thispagestyle{fancy}
\maketitle
\tableofcontents

\section{Premise}

\section{Caracters}

\subsection{Kelidis}
Commander Kelidis, or Clyde, is a fully upgraded Protogen with grey \say{fur}. He actually
has his fur in a gradient going from top to bottem starting with light blue and enging in
purple. He has four ears. The front pair are pink inside and have cyan tufts of fur. The
back pair is just dark grey like his legs. His feet \(boots?\) have a green stripe wich is
related to his rocket boots. He has no armor and wears a blue and orange scarf to hide his
neck fur so he can look more like a human. He wears a grey hoodie with a horazontal black 
stripe on it twards the bottom in an attempt to hide his \emph{literall} true colors. He
used to have a tail that was a basic thin curve-point like shape that was orange with a white tip.
He lost it in the Mosphere-Persius war. He does not have a pulse but he is still alive
because of various uppgrades he got that bought him enough time to take him to a lab.
Once he was there, they figured out how to rebuild him and thats how he met TEKNIQ.

\subsection{TEKNIQ}
TEKNIQ, \(\say{Tech Nick}\) is a basic Protogen with white fur and grey brackets. 
He dosn't have any magic powers or upgrades, he just wants to be himself. The 
problem is, Clyde keeps dragging him arround on hsi adventures. TEKNIQ is suposed 
to keep track of the GEMs and he is constantly reminding Clyde that he is technicly 
retired but Clyde persists on bring him along. He works for \say{ʁoiʒoapʁamoi}
\(\say{ROI-ZHOA-PHRAH-moy}\). Its a combonation of \say{The stars} and 
\say{Non-living-Protogen}. He makes gagets
\end{document}
